%! TEX root=../main.tex

\section{Responses}
  \subsection{Response 1}
    \begin{quotation}
      Although I wouldn’t say I hadn’t improved in it at all, I’d say that the
        most challenging skill to improve was the skill of asserting myself.
        The assignments in this course made me more aware of the skill itself
        and some ways I could improve it in feedback that was much more helpful
        and I think more engaging than reading off of a Helpline article. On the
        other hand I think my ability to be an engaged listener had drastically
        improved due to the same causes of reading feedback and reading some of
        the other content off this course’s pages.

      Of course the hardest challenge was COVID-19. It made finding people to
        interact with much more difficult and I often found myself trying to
        create meaningful encounters so I could practice assertion and
        engagement for the practice log. Some of the encounters that helped
        though were simple phone calls concerning my upcoming graduation, my
        transfer, calls with friends and the occasional meetings with some other
        friends and family friends.
    \end{quotation}

    \paragraph{This is a response to Lillian Morton on Post ID 43609215}
      Excellent response, Lillian! I regret that we were unable to get to know
        one another over the course of this class a bit more. I completely
        agree with you in regards to how tremendous an impact the Coronavirus
        COVID-19 Pandemic affected the ability for us to practice interpersonal
        communication skills. I was lucky enough to keep my job throughout the
        pandemic in an essential function (who knew Cannabis would be
        ``essential'' one of these days)!. I can tell you that even with the
        ability to see 600 customers a day and work with the same people over
        the course of three years, it is \textit{still} difficult to communicate
        because all you can see if someone's eyes and the masks tend to muffle
        communication, along with the large plexiglass we now use at our
        registers to limit the ability for sound to travel even further!
